\documentclass[a4paper,12pt]{article} %make sure that we are using 12 pt font
\usepackage{fancyhdr}
\usepackage[margin=2.5cm]{geometry}%rounded up from 1.87, just to be safe...
\usepackage{parskip}
%%\usepackage{times} %make sure that the times new roman is used
\usepackage{sectsty}
%%\raggedright



\begin{document}


\pagestyle{fancy}
%This puts your name at the top right, outside the margin
\lhead{CPSC 607: Biological Computation (Winter 2016)\\Project Documentation}
\rhead{Samiul Azam\\30 Apr. 2016}
 \renewcommand{\headrulewidth}{1pt}
\sectionfont{\fontsize{12}{15}\selectfont}
\vspace{2cm}


\section*{\\Phase 01: Database and Feature Generation}
............................................................................................................................................

In the command window of Matlab, type ``help $<$\verb|file_name.m|$>$'' to see the header documentation of my program scripts.\\
............................................................................................................................................

\textbf{Note 1:}\\\\
This folder have a sub-folder ``CLP\_Database'' that contains all the Candidate License Plates (License Plate (LP) + non-License Plate (non-LP) images). The CLP database is created using the license plate detection algorithm (ALPD) and the database of 565 vehicle images from the article~\cite{Aza16}. I didn't add the vehicle image database and the implementation of ALPD algorithm from the article~\cite{Aza16} (because it is not directly relate to this project and contains ten more files).  


............................................................................................................................................\\
\textbf{Note 2: }\\\\
This folder contains following main scripts. Go to Matlab Command Window and type the target main script (For example $>>$  \verb|CLP_info|) for execution.
\begin{itemize}
	\item \verb|CLP_info.m|   
		\begin{itemize}
		\item Read the main script header for more details.
		\item This program will provide you some statistical information about the (Candidate License Plate) CLP database.
		\item It generates a ``txt'' file named \verb|CLP_info_output.txt| (in the current directory) that contains the outputs.	
		\end{itemize}
	\item \verb|feature_gen.m|
		\begin{itemize}
			\item Read the main script header for more details.
			\item This program extracts HOG features from all the images in the CLP\_Database.  
			\item It generates following 6 ``mat'' files that contain the HOG features for three different resolutions (original, double and half) of LPs and Non-LPs.
				\begin{itemize}
					\item \verb|LP_1x.mat|
					\item \verb|LP_2x.mat|
					\item \verb|LP_hx.mat|
					\item \verb|nonLP_1x.mat|
					\item \verb|nonLP_2x.mat|
					\item \verb|nonLP_hx.mat|						
				\end{itemize}
		\end{itemize}
\end{itemize}

............................................................................................................................................\\

............................................................................................................................................\\
\textbf{Note 3: }\\
This folder contains following function script (You don't need to run it separately).
\begin{itemize}
	\item \verb|my_hog.m|
		\begin{itemize}
			\item Read the function header for more details.
			\item This function is used inside \verb|feature_gen.m|.
		\end{itemize}
\end{itemize}
............................................................................................................................................\\
In the command window of Matlab, type ``help $<$\verb|file_name.m|$>$'' to see the header documentation of my program scripts.\\
............................................................................................................................................
\begin{thebibliography}{99}
	
	\bibitem{Aza16} Azam, S., Islam, M. M., ``Automatic license plate detection in hazardous condition,'' Journal of Visual Communication and Image Representation, Elsevier, vol. 36, pp. 172-186, 2016.

	
\end{thebibliography}

\end{document}