\documentclass[a4paper,12pt]{article} %make sure that we are using 12 pt font
\usepackage{fancyhdr}
\usepackage[margin=2.5cm]{geometry}%rounded up from 1.87, just to be safe...
\usepackage{parskip}
%%\usepackage{times} %make sure that the times new roman is used
\usepackage{sectsty}
%%\raggedright



\begin{document}


\pagestyle{fancy}
%This puts your name at the top right, outside the margin
\lhead{CPSC 607: Biological Computation (Winter 2016)\\Project Documentation}
\rhead{Samiul Azam\\30 Apr. 2016}
 \renewcommand{\headrulewidth}{1pt}
\sectionfont{\fontsize{12}{15}\selectfont}
\vspace{2cm}


\section*{\\Phase 06: Last Experiment}
............................................................................................................................................

In the command window of Matlab, type ``help $<$\verb|file_name.m|$>$'' to see the header documentation of my program scripts.\\
............................................................................................................................................

\textbf{Note 1:}\\\\
This folder contains following main script. Go to Matlab Command Window and type the target main script (For example $>>$  \verb|train_models|) for execution.
\begin{itemize}
	\item \verb|train_models.m|   
		\begin{itemize}
		\item Read the main script header for more details.
		\item This program will generate four trained classifiers (based on original size (1x) CLPs) for mixture of expert-models. The model files are as follows
		
			\begin{itemize}
				\item \verb|knn.mat|
				\item \verb|svm.mat|
				\item \verb|tree.mat|
				\item \verb|disa.mat|
				
			\end{itemize}
	\end{itemize}
		
	\item \verb|test_mixture.m|
		\begin{itemize}
		\item Read the main script header for more details.   	
		\item It generates a ``txt'' file named \verb|output.txt| (in the current directory) that contains the outputs (accuracies of the final mixture of expert-models for different sizes of CLPs).	
			
		\end{itemize}
		
\end{itemize}

............................................................................................................................................
\textbf{Note 2: }\\\\
This folder contains following function scripts (You don't need to run them separately).
\begin{itemize}
	
	\item \verb|mixture_fitness.m|
	\begin{itemize}
		\item Read the function header for more details.
		\item This function will give the accuracy (\%) of the mixture-model based on the provided weight vector (w) and selected resolution of the CLPs (S) as parameter. 
		\item This function is used inside \verb|test_mixture.m|. 

	\end{itemize}

	\item \verb|my_svmclassify.m|
	\begin{itemize}
		\item Not my major contribution. I slightly modify the built-in matlab function to generate probability instead of `0' or `1' labels. 
		\item This function is used inside \verb|mixture_fitness.m|.
	\end{itemize}
	\item \verb|my_svmdecision.m|
	\begin{itemize}
		\item Not my major contribution. I slightly modify the built-in matlab function to generate probability instead of `0' or `1' labels. 
		\item This function is used inside \verb|my_svmclassify.m|.
	\end{itemize}
	
\end{itemize}
............................................................................................................................................\\
In the command window of Matlab, type ``help $<$\verb|file_name.m|$>$'' to see the header documentation of my program scripts.\\
............................................................................................................................................

\end{document}